A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-30 1_intro.tex
lil abstract change

FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
A common strategy to accurately manufacture a given 3D model is to extrude along a contour-following path,
because the position and shape of the toolpath can be controlled relatively accurately.
Filling up a shape using parallel straight lines would expose defects of the size of the nozzle ($\pm 10^2 \mu$), which is generally an order of magnitude larger than the resolution of the positioning system ($\pm 10^1 \mu$).
Contour parallel extrusion therefore leads to a less bumpy outline shape than direction parallel extrusion does.

>>>>

FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
A common strategy to accurately manufacture a given 3D model is to extrude along a contour-following path,
because the position and shape of the toolpath can be controlled relatively accurately.
Filling up a shape using parallel straight lines would expose defects of the size of the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
Contour parallel extrusion therefore leads to a less bumpy outline shape than direction parallel extrusion does.
